Twists of supersymmetric gauge theories

### 2019-12-27 paper.tex
merge
Matter SUSY in all dimensions, 10d SYM update

\newcommand{\Cl}{\mathrm{Cl}}
\newcommand{\Dens}{\mathrm{Dens}}

@@

\begin{definition}
A \defterm{free BV theory} on a manifold $M$ is the data:
\begin{itemize}
\item a finite rank $\ZZ\times\ZZ/2$-graded vector bundle $E \to M$ equipped with an even differential operator of cohomological degree $+1$
\[
Q \colon \cE \to \cE [1] 
\]
such that $(1)$: $Q^2 = 0$ and $(2)$: the pair $(\cE , Q)$ is an elliptic complex;
\item a map of bundles
\[
\omega\colon E \otimes E \to \Dens_M [-1]
\]
that is
\begin{enumerate}
\item[$(1)$] fiberwise nondegenerate,
\item[$(2)$] graded skew symmetric, and
\item[$(3)$] satisfies $\int_M \omega\<e_0, Q e_1\> = (-1)^{|e_0|} \int_M \omega(Q e_0, e_1)$ where $e_i$ are compactly supported sections of $E$ .
\end{enumerate}
\end{itemize}
\end{definition}

@@

\begin{definition}
A \defterm{morphism} $F\colon (E, Q, \omega, I) \rightsquigarrow (E', Q', \omega', I')$ of classical field theories over the same manifold $M$ is a nonlinear map of vector bundles $E\rightsquigarrow E'$, i.e. a collection $F=\sum_{n\geq 1}^\infty F$ of poly-differential operators $F_n\colon \Sym^n(E)\rightarrow E'$, that intertwines the differentials $Q, Q'$, the pairings $\omega, \omega'$, and the interactions $I,I'$. A morphism is an \defterm{equivalence} if the map $F_1\colon (\cE, Q)\rightarrow (\cE', Q')$ is a quasi-isomorphism.
\end{definition}

@@

@@

Notice that the BV complex we defined in the previous section, Equation (\ref{bvcplx}), is the global sections of the factorization algebra along $M$.
The BV complex can be thought of as the complex of functions on the derived critical locus of the action functional.
It makes sense to restrict fields to any open set $U \subset M$. 
Thus, likewise, the value of the factorization algebra on an open set $U \subset M$ can be interpreted as functions on the critical locus of the action functional where we restrict the theory to $U$.

@@

Fix a Lie algebra $\fg$ equipped with a nondegenerate symmetric bilinear pairing $\langle -, -\rangle$ and a spinorial representation $\Sigma$ of $\so(V)$ with an $\so(V)$-equivariant pairing $\Gamma \colon \Sym^2(\Sigma)\to V$. We define the Clifford action $\rho\colon V\rightarrow \hom(\Sigma, \Sigma^*)$ by
\begin{equation}
(\rho(v) Q_1, Q_2) = (v, \Gamma(Q_1, Q_2))
\label{eq:Gammaspinorpairing}
\end{equation}
for any $Q_1, Q_2\in\Sigma$ and $v\in V$.

The fields of Yang--Mills theory are as follows:
\begin{itemize}
\item A connection $A \in \Omega^1(V_\RR; \fg)$ on the trivial bundle.

@@

The BRST action is given by
\[S(A, \lambda) = \int_{V_\RR} \left\langle -\frac{1}{4} F_A \wedge \ast F_A + \frac{1}{2}(\lambda, \sd D_A \lambda)\right\rangle.\]

The associated BV theory $(E, Q, \omega, I)$ is given as follows (see also \cite[Section 3.1]{ElliottYoo1}). Let $A^*, \lambda^*, c^*$ be the antifields corresponding to $A, \lambda, c$ respectively. The bundle of BV fields is
\[E = \Omega^1(V_\RR; \fg)\oplus \Omega^0(V_\RR; \Pi\Sigma\otimes \fg)\oplus \Omega^0(V_\RR; \fg)[1] \oplus \Omega^{n-1}(V_\RR; \fg^*)[-1]\oplus \Omega^n(V_\RR; \Pi\Sigma^*\otimes \fg^*)[-1]\oplus \Omega^n(V_\RR; \fg^*)[-2].\]
The pairing $\omega$ on $E$ is induced by the evaluation pairings $\gg^*\otimes \gg\rightarrow \CC$ and $\Sigma^*\otimes\Sigma\rightarrow\CC$. The BV action is given by
\[S_{BV} = \int_{V_\RR} \left\langle -\frac{1}{4} F_A \wedge \ast F_A + \frac{1}{2}(\lambda, \sd D_A \lambda)\right\rangle - (\d_A c, A^*) + ([\lambda, c], \lambda^*) + \frac{1}{2}([c, c], c^*).\]

@@

@@

Let $V_\RR = \RR^n$ endowed with its nondegenerate bilinear form and $V=V_\RR\otimes_\RR\CC$ its complexification. Consider the Lie algebra $\so(V)$. Let us recall the following facts:
\begin{itemize}
\item If $n$ is odd, $\so(V)$ has a distinguished fundamental representation called the \defterm{spin} representation $S$.

@@

For certain choices of the spinorial representation, the Yang--Mills theory from Section \ref{YM_section} admits an action of supersymmetry. In this section we consider pairs consisting of a supersymmetry algebra and an instance of Yang--Mills theory with matter, in one of the following four situations:
\begin{itemize}
 \item Dimension $n=3$ with $\Sigma = S$, the 2-dimensional Dirac representation.
 \item Dimension $n=4$ with $\Sigma = S_+ \oplus S_-$, 4-dimensional Dirac representation.
 \item Dimension $n=6$ with $\Sigma = S_+ \otimes W$ where $W$ is a 2-dimensional symplectic vector space, the 8-dimensional symplectic Weyl representation.
 \item Dimension $n=10$ with $\Sigma = S_+$, the 16-dimensional Weyl representation.
\end{itemize}
These correspond to the 3d $\cN=1$, 4d $\cN=1$, 6d $\cN=(1, 0)$ and 10d $\cN=(1, 0)$ vector multiplets respectively.

We will construct, in each of these cases, an $L_\infty$ action of the super Lie algebra $\mf{A}$ on the theory. Following Definition \ref{infinitesimal_action_def}, we have to construct a collection of functionals $I^{(1)}, I^{(2)}, \dots$, where $I^{(k)}\colon \mf{A}^{\otimes k}\rightarrow \oloc(\cE)$, satisfying the classical master equation. The supersymmetry action we construct will extend the Poincar\'{e} action from \eqref{eq:Poincareaction}, so we just have to specify the values of $I^{(k)}$ on the supersymmetry generators in $\Sigma$.

Recall that $\Gamma\colon\Sym^2(\Sigma)\rightarrow V$ gives rise to an action map
\[\rho\colon V\otimes \Sigma\longrightarrow \Sigma^*\]
by \eqref{eq:Gammaspinorpairing}. We may also identify $\wedge^2(V)\rightarrow \so(V)$ via
\[\omega\mapsto (w\mapsto -2\iota_{(w, -)} \omega).\]
This gives rise to an action map
\[\wedge^2(V)\otimes \Sigma\longrightarrow \Sigma\]
of two-forms on spinors. Finally, we choose a pairing $\Gamma\colon \Sym^2(\Sigma^*)\rightarrow V$ which again induces an action map $\rho\colon V\otimes \Sigma^*\rightarrow \Sigma$ which satisfies the Clifford relation
\[\rho(v_1)\rho(v_2) + \rho(v_2)\rho(v_1) = 2(v_1, v_2)\]
on $\Sigma$ and $\Sigma^*$.

The resulting action $\wedge^2(V)\otimes \Sigma\rightarrow \Sigma$ then coincides with the original action of $\so(V)$ on the spinorial representation $\Sigma$.

\begin{prop}
One has the following:
\begin{enumerate}
\item For $X\in\wedge^2(V)$ and $Q_1,Q_2\in\Sigma$ we have
\[\Gamma(Q_1, \rho(X) Q_2) + \Gamma(Q_2, \rho(X) Q_1) = -2\iota_{\Gamma(Q_1, Q_2)} X.\]

\item Suppose $Q_1,Q_2\in\Sigma$ and $\lambda\in\Gamma(M, \Sigma\otimes \fg)$. Then
\[\sd{D}_A\rho(\Gamma(Q_1, \lambda)) Q_2 = \rho(d_A \Gamma(Q_1, \lambda)) Q_2 + (Q_1, \sd{D}_A \lambda) Q_2.\]

\item Suppose $Q\in\Sigma$ and $X\in\Omega^2(M; \fg)$. Then
\[\sd{D}_A(\rho(X) Q) = \rho(d_A X)Q + (-1)^n\rho(\ast d_A\ast X) Q.\]
\end{enumerate}
\label{prop:cliffordactionproperties}
\end{prop}

In addition, we have the following important property of the $\Gamma$-pairing which holds in the above cases. This was proved in \cite{Schray} in dimension 10 and explained in \cite{BaezHuerta} using division algebras in all dimensions.

\begin{prop}
Suppose $Q_1, Q_2, Q_3\in\Sigma$. Then
\[\rho(\Gamma(Q_1, Q_2))Q_3 + \rho(\Gamma(Q_2, Q_3))Q_1 + \rho(\Gamma(Q_3, Q_1))Q_2 = 0.\]
\label{prop:3psi}
\end{prop}

The second term gives
\begin{align*}
\{S_{BV}^2, I^{(1)}(Q)\} &= -\frac{1}{2}(\lambda, \rho(\Gamma(Q, \lambda))\lambda) + \frac{1}{2}(\rho(F_A) Q, \sd{D}_A\lambda) \\
&= -\frac{1}{2}(\Gamma(Q, \lambda), \Gamma(\lambda, \lambda))  - \frac{1}{2}(\lambda, \sd{D}_A(\rho(F_A) Q)) \\
&= -\frac{1}{2}(\Gamma(Q, \lambda), \Gamma(\lambda, \lambda)) - \frac{1}{2} (-1)^n (\lambda, \rho(\ast d_A\ast F_A) Q),
\end{align*}
where we have used Proposition \ref{prop:cliffordactionproperties} (property (3)) and the Bianchi identity in the last line.

By \eqref{eq:Gammaspinorpairing} and Proposition \ref{prop:3psi} we have $(\Gamma(Q, \lambda), \Gamma(\lambda, \lambda)) = 0$, so $\{S_{BV}^1 + S_{BV}^2, I^{(1)}(Q)\} = 0$.

The individual terms are
\begin{align*}
\{I^{(1)}, I^{(1)}\}(Q_1, Q_2) = &-2\{I^{(1)}(Q_1), I^{(1)}(Q_2)\} \\
= &-(\rho(d_A \Gamma(Q_1, \lambda)) Q_2, \lambda^*) - \Gamma(Q_2, \rho(F_A)Q_1)\wedge A^* \\
&-(\rho(d_A \Gamma(Q_2, \lambda)) Q_1, \lambda^*) - \Gamma(Q_1, \rho(F_A)Q_2)\wedge A^*,
\end{align*}
\begin{align*}
(\d_{CE} I^{(1)})(Q_1, Q_2) &= I^{(1)}(\Gamma(Q_1, Q_2)) \\
&= -L_{\Gamma(Q_1, Q_2)}(A)\wedge A^* -(\Gamma(Q_1, Q_2).\lambda, \lambda^*) - (\Gamma(Q_1, Q_2).c) c^*
\end{align*}
and
\begin{align*}
\{S_{BV}, I^{(2)}(Q_1, Q_2)\} = &-\frac{1}{2}(Q_2, \lambda^*)(Q_1, \sd{D}_A \lambda + [c, \lambda^*]) - \frac{1}{2}(Q_1, \lambda^*)(Q_2, \sd{D}_A \lambda + [c, \lambda^*]) \\
&+\frac{1}{2}(\Gamma(Q_1, Q_2), \Gamma(\lambda^*, \sd{D}_A \lambda + [c, \lambda^*])) + \iota_{\Gamma(Q_1, Q_2)}(d_A c) c^* + d_A\iota_{\Gamma(Q_1, Q_2)} A\wedge A^* \\
&+ ([\lambda, \iota_{\Gamma(Q_1, Q_2)}A], \lambda^*) - [\iota_{\Gamma(Q_1, Q_2)} A, c] c^*
\end{align*}
The total coefficient in front of $A^*$ is
\[-\frac{1}{2}\Gamma(Q_1, \rho(F_A)Q_2) - \frac{1}{2}\Gamma(Q_2, \rho(F_A) Q_1) - L_{\Gamma(Q_1, Q_2)} A + d_A \iota_{\Gamma(Q_1, Q_2)} A.\]
Using Proposition \ref{prop:cliffordactionproperties} (property (1)) we get that the sum of the first two terms is $\iota_{\Gamma(Q_1, Q_2)}F_A$ which cancels the last two terms.

The total coefficient in front of $\lambda^*$ is
\begin{align*}
&-\frac{1}{2}\rho(d_A \Gamma(Q_1, \lambda))Q_2 -\frac{1}{2}\rho(d_A \Gamma(Q_2, \lambda))Q_1 - \Gamma(Q_1, Q_2).\lambda \\
&+ \frac{1}{2}\rho(\Gamma(Q_1, Q_2))\sd{D}_A\lambda - \frac{1}{2}(Q_2, \sd{D}_A\lambda) Q_1 -\frac{1}{2}(Q_1, \sd{D}_A\lambda) Q_2 + [\lambda, (\Gamma(Q_1, Q_2), A)]
\end{align*}
Using Proposition \ref{prop:cliffordactionproperties} (property (2)) the first, second, fifth and sixth terms combine to
\[-\frac{1}{2} \sd{D}_A\rho(\Gamma(Q_1, \lambda))Q_2 - \frac{1}{2} \sd{D}_A\rho(\Gamma(Q_2, \lambda)) Q_1\]
which is equal to $\frac{1}{2} \sd{D}_A \rho(\Gamma(Q_1, Q_2))\lambda$ by Proposition \ref{prop:3psi}. Using the Clifford relation this term cancels the rest of the terms.
\end{proof}

$\{I^{(1)}, I^{(2)}\}$ is obtained by cyclically symmetrizing the above expression. By Proposition \ref{prop:3psi} the cyclic symmetrization of the term with $c^*$ is zero. The Clifford relation implies that
\begin{align*}
\frac{1}{2} (\Gamma(Q_2, Q_3), \Gamma(\rho(A^*) Q_1, \lambda^*)) &= -\frac{1}{2}(\Gamma(Q_2, Q_3), \Gamma(\rho(A^*)\lambda^*, Q_1)) + (\Gamma(Q_2, Q_3), A^*) (Q_1, \lambda^*) \\
&= -\frac{1}{2}(\rho(\Gamma(Q_2, Q_3)) Q_1, \rho(A^*)\lambda^*) + (\Gamma(Q_2, Q_3), A^*) (Q_1, \lambda^*).
\end{align*}
Therefore, again using Proposition \ref{prop:3psi} we see that the cyclic symmetrization of the terms with $A^*$ vanishes.
\end{proof}

We can deduce supersymmetry for other super Yang-Mills theories using dimensional reduction, specifically Proposition \ref{dim_red_SUSY_prop}.
\begin{corollary}
Let $n$ be one of the special dimensions $3,4,6$ or 10, and choose $m < n$.  Let $\Sigma'$ be the $\so(m)$ representation obtained by restriction of the $\so(n)$ representation $\Sigma$.  Then the super Poincar\'e algebra
\[\mf A' = \mf{iso}(m) \oplus \Pi \Sigma',\]
obtained by restricting the $n$-dimensional super Poincar\'e algebra associated to $\Sigma$, acts on the $m$-dimensional super Yang-Mills theory $\mf L'$ with matter representation $\Sigma'$.
\end{corollary}

\begin{remark}
We can further include the action of at least a subalgebra of the algebra of R-symmetries in each example. \chris{quantify which}
\end{remark}

\subsection{Supersymmetric matter}

The action of supersymmetry is given by a linear and quadratic functional:
\begin{align*}
I^{(1)} (Q) & = \int (\phi^*, (Q, \psi))_{W_+ \otimes U} + (\psi^*, \rho(\d \phi) Q)_U \\
I^{(2)} (Q_1 , Q_2) & =  \int \frac{1}{4}(\Gamma(Q_1, Q_2)_{W_+} , \Gamma(\psi^*, \psi^*)_{U}) 
%\textcolor{red}{-\frac{1}{2} (Q_1, \psi^*)_U(Q_2, \psi^*)_U  }.
\end{align*}
where $Q, Q_1,Q_2 \in \Sigma = S_+ \otimes W_+$. 
We point out some conventions in the definition of $I^{(2)}$. 
Define $\Gamma (Q_1,Q_2)_{W_+} \in V$ as the image of $Q_1 \otimes Q_2$ under the composition
\[
\Sigma \otimes \Sigma = (S_+ \otimes W_+) \otimes (S_+ \otimes W_+) \cong (S_+ \otimes S_+) \otimes (W_+ \otimes W_+) \xto{\Gamma \otimes \omega_{W_+}} V .
\]

\begin{lemma} 
One has $\{S, I^{(1)}\} (Q) = 0$ for all $Q \in \Sigma$. 
\end{lemma}
\begin{proof}
Observe
\[
- \{\d \phi \wedge * \d \phi, \phi^*  (Q, \psi) \} = - 2 \d (Q, \psi) \wedge * \d \phi .
\]
and
\[
\{(\psi, \sd \dd \psi) , (\psi^*, \rho(\d \phi) Q) \} = 2 (\rho(\d \phi) Q, \sd \dd \psi) \d^4 x .
\]
The sum of these two terms is zero by Lemma \ref{lem: oneform}. 
\end{proof}

Next, we collect all terms in Equation (\ref{CMEhyper3}) proportional to $\psi^*$:
\begin{equation}\label{psistar}
\begin{array}{cccc}
& - & \displaystyle \frac{1}{2} \rho(\d(Q_1,\psi))Q_2 - \frac{1}{2} \rho(\d(Q_2, \psi)) Q_1 - \Gamma(Q_1,Q_2) . \psi
\\ 
& + &\displaystyle \frac{1}{2} \rho(\Gamma(Q_1,Q_2)) \sd \dd \psi 
%\textcolor{red}{ - \frac{1}{2} (Q_2, \sd \dd \psi)Q_1 - \frac{1}{2} (Q_1, \sd \dd \psi)Q_2}
\end{array}
\end{equation}
By Proposition \ref{prop:cliffordactionproperties} item (3), the first and second terms can be written as:
\[
- \frac{1}{2} \rho(\d(Q_1,\psi))Q_2 - \frac{1}{2} \rho(\d(Q_2, \psi)) Q_1 = - \frac{1}{2} \sd \dd \left( (Q_1, \psi)Q_2 + (Q_2 , \psi)Q_1 \right).
\]
Applying Proposition \ref{prop: new3psi}, to $Q_3 = \psi$, this becomes $-\frac{1}{2} \sd \dd \rho(\Gamma(Q_1,Q_2) \psi)$. 
Finally, by the Clifford identity, the sum of this term with the fourth term in (\ref{psistar}) is precisely $\Gamma(Q_1,Q_2) . \psi$.
So the expression (\ref{psistar}) is identically zero. 
\end{proof}

\begin{lemma}
\[\{I^{(1)}, I^{(2)}\}(Q_1, Q_2, Q_3) = 0\]
for every $Q_1, Q_2, Q_3\in \Sigma$.
\end{lemma}
\begin{proof}
We have
\begin{align*}
\{I^{(1)}(Q_1), I^{(2)}(Q_2, Q_3)\} & = \frac{1}{2} (\Gamma(Q_2, Q_3), \Gamma(\psi^*, \phi^* Q_1)) \\ & = (\psi^*, \phi^* \rho(\Gamma(Q_2,Q_3)) Q_1)  .
\end{align*}
The expression
$\{I^{(1)}, I^{(2)}\}(Q_1,Q_2,Q_3$ is obtained by cyclically symmetrizing the above expression. By Proposition \ref{prop:3psi} the cyclic symmetrization is identically zero.
\end{proof}

@@

\begin{prop}
Fix a twisting datum $(Q, \alpha)$, where $\Gamma_V(Q, Q) = 0$. Then the dimensional reduction of the twist of the classical field theory $E$ is isomorphic to the twist of the dimensional reduction of $E$.
\end{prop}

@@

>>>>

\newcommand{\Cl}{\mathrm{Cl}}
\newcommand{\Dens}{\mathrm{Dens}}
\renewcommand{\Re}{\mathrm{Re}}

@@

\begin{definition}
A \defterm{free BV theory} on a manifold $M$ is the data:
\begin{itemize}
\item a finite rank $\ZZ\times\ZZ/2$-graded vector bundle $E \to M$ equipped with an even differential operator of cohomological degree $+1$
\[
Q \colon \cE \to \cE [1] 
\]
such that $(1)$: $Q^2 = 0$ and $(2)$: the pair $(\cE , Q)$ is an elliptic complex;
\item a map of bundles
\[
\omega\colon E \otimes E \to \Dens_M [-1]
\]
that is
\begin{enumerate}
\item[$(1)$] fiberwise nondegenerate,
\item[$(2)$] graded skew symmetric, and
\item[$(3)$] satisfies $\int_M \omega(e_0, Q e_1) = (-1)^{|e_0|} \int_M \omega(Q e_0, e_1)$ where $e_i$ are compactly supported sections of $E$ .
\end{enumerate}
\end{itemize}
\end{definition}

@@

\begin{definition}
A \defterm{morphism} $F\colon (E, Q, \omega, I) \rightsquigarrow (E', Q', \omega', I')$ of classical field theories over the same manifold $M$ is a nonlinear map of vector bundles $E\rightsquigarrow E'$, i.e. a collection $F=\sum_{n\geq 1}^\infty F$ of poly-differential operators $F_n\colon \Sym^n(E)\rightarrow E'$, that intertwines the differentials $Q, Q'$, the pairings $\omega, \omega'$, and the interactions $I,I'$. A morphism is a \defterm{perturbative equivalence} if the map $F_1\colon (\cE, Q)\rightarrow (\cE', Q')$ is a quasi-isomorphism. A classical field theory is \defterm{perturbatively trivial} if it is perturbatively equivalent to the zero theory.
\end{definition}

@@

We will now describe two primitive examples of equivalences of classical field theories which will be useful in simplifying twisted theories. First, we consider the process of integrating out an auxiliary field.

\begin{prop}
Fix a volume form $\dvol_M$ on $M$. Suppose $(E, Q, \omega, I)$ is a classical field theory, where $E\cong E_0\oplus (\cO_M\oplus \Dens_M[-1])$ with the symplectic pairing $\omega$ given by a sum of a symplectic pairing $\omega_0$ on $E_0$ and the standard symplectic pairing on the second summand. Denote by $\phi$ a section of $\cO_M$ and by $\phi^*$ a section of $\Dens_M[-1]$. Suppose the BV action is
\[S_{BV} = S_0 + \frac{1}{2} \int \dvol_M (\phi^2 - 2\phi S_1),\]
where $S_0$ and $S_1$ are independent of $\phi$. Then the theory $(E, Q, \omega, I)$ is perturbatively equivalent to the theory $(E_0, Q_0, \omega_0, I_0)$ with the BV action $S_0 - S_1^2/2$, where we set $\phi^* = 0$ and $\phi = S_1$.
\label{prop:integrateoutfield}
\end{prop}
\begin{proof}
\pavel{The map $E_0\rightarrow E$ is obviously compatible with all the structures.}
\end{proof}

We may also remove a trivial BRST doublet.

\begin{prop}
Suppose $(E, Q, \omega, I)$ is a classical field theory, $F\rightarrow M$ is a graded vector bundle, such that $E\cong E_0\oplus F\oplus F^![-1]\oplus F^!\oplus F[-1]$. Denote by $\phi, \phi^*$ sections of $F,F^![-1]$ and by $\psi, \psi^*$ sections of $F^!, F[-1]$. Suppose
\[Q\phi + \{I, \phi\} = \psi - F_\psi,\qquad Q\psi^* + \{I, \psi^*\} = \phi^* - F_{\phi^*},\]
where $F_\psi$ is independent of $\psi$ and $F_{\phi^*}$ is independent of $\phi^*$. Then the theory $(E, Q, \omega, I)$ is perturbatively equivalent to the theory $(E_0, Q_0, \omega_0, I_0)$ with the BV action obtained by setting $\phi = 0, \phi^* = F_{\phi^*}, \psi = F_\psi, \psi^* = 0$ in the original BV action.
\label{prop:BRSTdoublet}
\end{prop}
\begin{proof}
\end{proof}

@@

Notice that the BV complex we defined in the previous section, Equation (\ref{bvcplx}), is the global sections of the factorization algebra along $M$.
The BV complex can be thought of as the complex of functions on the derived critical locus of the BRST action.
It makes sense to restrict fields to any open set $U \subset M$. 
Thus, likewise, the value of the factorization algebra on an open set $U \subset M$ can be interpreted as functions on the critical locus of the BRST action where we restrict the theory to $U$.

@@

Fix a Lie algebra $\fg$ equipped with a nondegenerate symmetric bilinear pairing $\langle -, -\rangle$ and a Clifford module $\Sigma\oplus \Sigma^*$ as in Section \ref{sect:spinors}. The fields of the Yang--Mills theory are as follows:
\begin{itemize}
\item A connection $A \in \Omega^1(V_\RR; \fg)$ on the trivial bundle.

@@

The BRST action is given by
\[S(A, \lambda) = \int_{V_\RR} \left\langle -\frac{1}{4} F_A \wedge \ast F_A + \frac{1}{2}(\lambda, \sd \dd_A \lambda)\right\rangle.\]

The associated BV theory $(E, Q, \omega, I)$ is given as follows (see also \cite[Section 3.1]{ElliottYoo1}). Let $A^*, \lambda^*, c^*$ be the antifields corresponding to $A, \lambda, c$ respectively. The bundle of BV fields is
\[E = \Omega^1(V_\RR; \fg)\oplus \Omega^0(V_\RR; \Pi\Sigma\otimes \fg)\oplus \Omega^0(V_\RR; \fg)[1] \oplus \Omega^{n-1}(V_\RR; \fg^*)[-1]\oplus \Omega^n(V_\RR; \Pi\Sigma^*\otimes \fg^*)[-1]\oplus \Omega^n(V_\RR; \fg^*)[-2].\]
The pairing $\omega$ on $E$ is induced by the evaluation pairings $\gg^*\otimes \gg\rightarrow \CC$ and $\Sigma^*\otimes\Sigma\rightarrow\CC$. The BV action is given by
\begin{equation}
S_{BV} = \int_{V_\RR} \left\langle -\frac{1}{4} F_A \wedge \ast F_A + \frac{1}{2}(\lambda, \sd\dd_A \lambda)\right\rangle - (\d_A c, A^*) + ([\lambda, c], \lambda^*) + \frac{1}{2}([c, c], c^*).
\label{eq:YMBVaction}
\end{equation}

@@

\begin{remark}
Therefore, it makes sense to talk about ``the'' dimensional reduction of a classical field theory along the projection $p \colon N \times \RR \to N$: there exists a dimensional reduction which is unique up to a canonical isomorphism.
\end{remark}

@@

Let $V_\RR = \RR^n$ endowed with a nondegenerate symmetric bilinear form and $V=V_\RR\otimes_\RR\CC$ its complexification. Consider the Lie algebra $\so(V)$. Let us recall the following facts:
\begin{itemize}
\item If $n$ is odd, $\so(V)$ has a distinguished fundamental representation called the \defterm{spin} representation $S$.

@@

\subsection{Division algebras and supersymmetry}
\label{sect:divisionalgebras}

We will now recall a relationship between certain ``minimal'' supersymmetry algebras and division algebras. Our treatment will essentially follow \cite{BaezHuerta}.

Let $A_\RR$ be a (possibly non-associative) real algebra equipped with an antiinvolution $\sigma\colon A_\RR\rightarrow A_\RR$. We make the following assumptions:
\begin{enumerate}
\item The map $\Re(x)=x\mapsto (x + \sigma(x))/2$ defines a projector onto the subspace of $A_\RR$ spanned by the unit.

\item By the previous assumption we have a quadratic form $x\sigma(x)\colon A_\RR\rightarrow \RR$. We assume that it is nondegenerate.
\end{enumerate}

For a $2\times 2$-matrix $M$ with entries in $A_\RR$ we define its hermitian adjoint $M^\dagger$ by transposing the matrix and applying $\sigma$ to the entries. We define $V_\RR$ to be the space of $2\times 2$ Hermitian matrices with values in $A_\RR$, so that $\dim(V_\RR) = \dim(A_\RR) + 2$. $V_\RR$ carries a nondegenerate quadratic form given by $M\mapsto -\det(M)$. Moreover, it carries an orthogonal involution $\widetilde{M} = M - \tr(M)\cdot 1$.

We denote the complexification of $A_\RR$ by $A=A\otimes_\RR \CC$ and extend $\sigma$ $\CC$-linearly to $A$. So, the complexification $V=V\otimes_\RR\CC$ is the space of $2\times 2$ Hermitian matrices with values in $A$.

Given a left $A$-module, we may turn it into a right $A$-module via the antiinvolution $\sigma\colon A\rightarrow A$. Since $A$ is a Frobenius algebra, we have the following basic construction

\begin{lemma}
Suppose $M$ is a left $A$-module and $N$ a right $A$-module equipped with a nondegenerate pairing $(-, -)\colon M\otimes N\rightarrow \CC$ satisfying $(am, n) = (m, na)$ for every $a\in A$, $m\in M$ and $n\in N$. Then there is a unique map $(-, -)^A\colon M\otimes N\rightarrow A$ of $(A, A)$-bimodules whose real part is $(-, -)$.
\label{lm:extendpairing}
\end{lemma}

Let $\Sigma=A\oplus A$ and $\Sigma^* = A\oplus A$. We have action maps
\[V\otimes \Sigma\rightarrow \Sigma^*,\qquad V\otimes \Sigma^*\rightarrow \Sigma\]
given, respectively, by
\[\rho(M)Q = M Q,\qquad \rho(M)Q = \widetilde{M} Q.\]

The following is proved in \cite[Proposition 6]{BaezHuerta}.

\begin{prop}
The action maps $V\otimes \Sigma\rightarrow \Sigma^*$ and $V\otimes \Sigma^*\rightarrow \Sigma$ satisfy the Clifford relation
\[\rho(M)\rho(M) = -\det(M)\cdot 1.\]
\end{prop}

We have a nondegenerate scalar spinorial pairing
\[\Sigma\otimes \Sigma^*\longrightarrow \CC\]
given by
\[(Q_1, Q_2) = \Re(Q_1^\dagger Q_2).\]
It obviously satisfies $(Q_1 \sigma(a), Q_2) = (Q_1, Q_2 a)$. The extension to an $A$-valued pairing provided by Lemma \ref{lm:extendpairing} is given by
\[(Q_1, Q_2)^A = Q_1^\dagger Q_2.\]

By duality we obtain maps $\Gamma\colon\Sym^2(\Sigma)\rightarrow V$ and $\Gamma\colon \Sym^2(\Sigma^*)\rightarrow V$ given, respectively, by
\[\Gamma(Q_1, Q_2) = \widetilde{Q_1Q_2^\dagger + Q_2Q_1^\dagger},\qquad \Gamma(Q_1, Q_2) = Q_1Q_2^\dagger + Q_2Q_1^\dagger.\]

We will now state two important properties of $\Gamma$ and the spinorial pairing. The following statement was proved in \cite[Theorem 11]{BaezHuerta} (see also \cite{Schray} for the case $\dim(V)=10$).

\begin{thm}
Suppose $A$ is alternative, i.e. $a\otimes b\otimes c\mapsto (ab)c - a(bc)$ is completely antisymmetric. For $Q_1, Q_2, Q_3\in\Sigma$ we have
\[\rho(\Gamma(Q_1, Q_2))Q_3 + \rho(\Gamma(Q_2, Q_3))Q_1 + \rho(\Gamma(Q_2, Q_3))Q_1 = 0.\]
\label{thm:3psi}
\end{thm}

If we moreover assume $A$ is associative, there is a relationship between the scalar spinorial pairing and $\Gamma$.

\begin{thm}
Suppose $A$ is associative. For $Q_1, Q_2\in\Sigma$ and $Q_3\in\Sigma^*$ we have
\[Q_1(Q_2, Q_3)^A + Q_2(Q_1, Q_3)^A = \rho(\Gamma(Q_1, Q_2)) Q_3.\]
\label{thm:matter3psi}
\end{thm}
\begin{proof}
The right-hand side is
\[(Q_1Q_2^\dagger + Q_2Q_1^\dagger)Q_3\]
which by associativity can be rewritten as
\[Q_1(Q_2^\dagger Q_3) + Q_2(Q_1^\dagger Q_3)\]
which is the left-hand side.
\end{proof}

We will be interested in the following four examples:
\begin{enumerate}
\item $A_\RR = \RR$. We have $\dim(V) = 3$ and $\Sigma$ is the spin representation of $\Spin(3)$ (3d $\mc N=1$ supersymmetry).

\item $A_\RR = \CC$. We have $A = \CC[x]/(x^2+1)$ with $\sigma(x) = -x$. Moreover, $\dim(V) = 4$ and $\Sigma=S_+\oplus S_-$ is the sum of semi-spin representations (4d $\mc N=1$ supersymmetry).

\item $A_\RR = \mathbb{H}$. We have $A=\eend(W_+)$, where $W_+$ is a two-dimensional symplectic vector space with $\sigma$ given by the dual operator. Moreover, $\dim(V) = 6$ and $\Sigma = S_+\oplus W_+$ (6d $\mc N=(1, 0)$ supersymmetry).

\item $A_\RR = \mathbb{O}$. We have $\dim(V) = 10$ and $\Sigma = S_+$ is a semi-spin representation (10d $\mc N=(1, 0)$ supersymmetry).
\end{enumerate}

All four examples are alternative, while the first three examples are moreover associative.

@@

\begin{prop}
Fix a twisting datum $(Q, \alpha)$, where $\Gamma_V(Q, Q) = 0$. Then the dimensional reduction of the twist of the classical field theory $E$ is isomorphic to the twist of the dimensional reduction of $E$.
\label{prop:twistdimensionalreduction}
\end{prop}

@@

\section{Supersymmetric Yang--Mills theories}

In this section we construct supersymmetry action on all super Yang--Mills theories. We have the following variants of the super Yang--Mills theory depending on $\dim(\Sigma)$:
\begin{itemize}
\item (16 supercharges). This theory exists in dimensions 2 through 10 and it depends on a Lie algebra $\fg$.

\item (8 supercharges). This theory exists in dimensions 2 through 6 and it depends on a Lie algebra $\fg$ together with a symplectic $\fg$-representation $U$. \pavel{Moment maps?}

\item (4 supercharges). This theory exists in dimensions 2 through 4 and it depends on a Lie algebra $\fg$ together with a $\fg$-representation $R$.

\item (2 supercharges). This theory exists in dimensions 2 through 3 and it depends on a Lie algebra $\fg$ together with an orthogonal $\fg$-representation $P$.
\end{itemize}

In each case the lower-dimensional theories are obtained by dimensional reduction from the theory in the highest dimension: for instance, 7d $\mc N=1$ super Yang--Mills (16 supercharges) is obtained by dimensional reduction from 10d $\mc N=(1, 0)$ super Yang--Mills. So, it will be enough to construct the supersymmetry action in these highest-dimensional theories.

Fix an \emph{alternative} algebra $A$ as in Section \ref{sect:divisionalgebras} and consider the associated vector space $V=A\oplus \CC^2$ and the spinorial representations $\Sigma$ and $\Sigma^*$. We will show that in this case the Yang--Mills theory from Section \ref{YM_section} admits an action of supersymmetry.

We will construct an $L_\infty$ action of the super Lie algebra $\mf{A}$ on the theory. Following Definition \ref{infinitesimal_action_def}, we have to construct a collection of functionals $I^{(1)}, I^{(2)}, \dots$, where $I^{(k)}\colon \mf{A}^{\otimes k}\rightarrow \oloc(\cE)$, satisfying the classical master equation. The supersymmetry action we construct will extend the Poincar\'{e} action from \eqref{eq:Poincareaction}, so we just have to specify the values of $I^{(k)}$ on the supersymmetry generators in $\Sigma$.
